---
title: "Pixel-level factor analysis of a Xenium breast cancer section from R"
format:
  html:
    toc: true
    embed-resources: true
execute:
  warning: false
---

This vignette drives the whole `punkst` workflow from R on a real Xenium breast
cancer section (about 42 million transcripts, a 313-gene panel) stored as a
SpatialData zarr store, and asks whether the learned factors recover recognisable
tissue compartments. Everything is done with punkstR functions and base R. The
package runs the `punkst` binary and a small export script with `system2()`; no
Python is called from this document.

**Requirements.** The chunks run only when all of these are available, and are
otherwise shown without being evaluated:

- `PUNKSTR_DEMO_ZARR`: path to the demonstration SpatialData store (a zarr v3
  store, so the Python that punkstR uses needs `spatialdata` >= 0.7).
- A built `punkst` binary (`PUNKST=/path/to/punkst`, or on the `PATH`). punkstR
  does not build it; see the README for the recipe.
- A Python with `spatialdata` (`PUNKST_PYTHON=/path/to/python`).
- Optionally `PUNKSTR_DEMO_WORKDIR`: a directory that keeps the intermediate
  files (about 2 GB), so re-rendering skips finished stages.

```{r}
#| label: setup
library(punkstR)

zarr <- Sys.getenv("PUNKSTR_DEMO_ZARR")
chk <- check_punkst_setup(quiet = TRUE)
can_run <- nzchar(zarr) && dir.exists(zarr) && chk@bin_ok && chk@python_ok
knitr::opts_chunk$set(eval = can_run, fig.width = 8, fig.height = 6, dpi = 110)
if (!can_run) message("Demo not evaluated: set PUNKSTR_DEMO_ZARR and check_punkst_setup().")

work <- Sys.getenv("PUNKSTR_DEMO_WORKDIR")
if (!nzchar(work)) work <- tempfile("punkstR_xenium_")
dir.create(work, showWarnings = FALSE, recursive = TRUE)
threads <- min(8L, parallel::detectCores())
```

```{r}
#| label: helpers
#| eval: true
# Small base-graphics helpers: one square marker per hexagon.
scale_col <- function(v, pal, vmin = min(v), vmax = max(v))
    pal[1L + round(pmin(pmax((v - vmin) / (vmax - vmin), 0), 1) * (length(pal) - 1L))]

spatial_plot <- function(x, y, col, main = "", cex = 0.12,
                         xlab = "x (um)", ylab = "y (um)", ...) {
    plot(x, y, col = col, pch = 15, cex = cex, asp = 1, ylim = rev(range(y)),
         xlab = xlab, ylab = ylab, main = main, ...)
}

heat <- function(m, main = "", zlim = range(m), pal = hcl.colors(50, "viridis"),
                 cex_row = 0.8, cex_col = 0.7) {
    op <- par(mar = c(9, 12, 2, 1)); on.exit(par(op))
    image(seq_len(ncol(m)), seq_len(nrow(m)), t(m[nrow(m):1, , drop = FALSE]),
          col = pal, zlim = zlim, axes = FALSE, xlab = "", ylab = "", main = main)
    axis(1, seq_len(ncol(m)), colnames(m), las = 2, cex.axis = cex_col, tick = FALSE)
    axis(2, seq_len(nrow(m)), rev(rownames(m)), las = 1, cex.axis = cex_row, tick = FALSE)
    box()
}
```

## 1. What is in the store?

`sdata_info()` summarises the store without loading the transcripts into R.

```{r}
info <- sdata_info(zarr, points_key = "transcripts")
tx <- info$points$transcripts
cat("SpatialData", info$spatialdata_version, "\n")
cat("points elements:", paste(names(info$points), collapse = ", "), "\n")
cat("images:", paste(names(info$images), collapse = ", "), "\n")
cat("tables:", paste(unlist(info$tables), collapse = ", "), "\n")
cat(sprintf("transcripts: %s rows; columns: %s\n", format(tx$rows, big.mark = ","),
            paste(unlist(tx$columns), collapse = ", ")))
```

## 2. Which coordinates does punkst need?

punkst works in microns. The `transcripts` element is registered in a single
coordinate system, `global`, through a scale transform, so exporting "the only
coordinate system" would silently change the units.

```{r}
g <- tx$transformations$global
scale <- g$scale[[1]]
um_per_px <- 1 / scale
width_px <- info$images$morphology_focus$sizes$x
cat("transform into 'global':", g$repr, "\n")
cat(sprintf("implied pixel size: %.4f um / px\n", um_per_px))
cat(sprintf("max stored x: %s\n", format(round(tx$max_x), big.mark = ",")))
cat(sprintf("image width:  %s px -> %s um at %.4f um/px\n",
            format(width_px, big.mark = ","),
            format(round(width_px * um_per_px), big.mark = ","), um_per_px))
```

The stored `x` maximum matches the image width *in microns*, so the stored
(intrinsic) coordinates are microns and `global` is image pixels.
`sdata_export()` therefore uses `coordinate_system = "intrinsic"` by default.

## 3. Export transcripts

We keep molecules with `qv >= 20`, the usual Xenium cut-off. Only `x`, `y` and
the feature name are written.

```{r}
tsv <- file.path(work, "transcripts.tsv")
system.time(sdata_export(zarr, tsv, coordinate_system = "intrinsic", min_qv = 20))
```

## 4. `pts2tiles`

```{r}
tiles <- punkst_pts2tiles(tsv, work, tile_size = 500, threads = threads)
feat <- punkst_read_features(tiles)
control_re <- xenium_control_regex()
is_ctrl <- grepl(control_re, feat$feature)
n_kept <- sum(feat$count)
cat(sprintf("kept %s of %s transcripts (%.1f%%) with qv >= 20\n",
            format(n_kept, big.mark = ","), format(tx$rows, big.mark = ","),
            100 * n_kept / tx$rows))
cat(sprintf("%d features: %d genes, %d control probes/codewords\n",
            nrow(feat), sum(!is_ctrl), sum(is_ctrl)))
cat(sprintf("control features hold %.2f%% of transcripts\n",
            100 * sum(feat$count[is_ctrl]) / sum(feat$count)))
```

## 5. `tiles2hex`

Transcripts are pooled into non-overlapping hexagons with a 12 µm centre-to-centre
spacing. We keep hexagons with at least 20 transcripts and randomise their order,
which online training benefits from.

```{r}
hex <- punkst_tiles2hex(tiles, hex_grid_dist = 12, min_count = 20,
                        randomize = TRUE, seed = 1, threads = threads)
hx <- punkst_read_hex(hex)
units <- hx$units
X <- hx$counts
dictionary <- colnames(X)
cat(sprintf("%s hexagons; median %.0f transcripts per hexagon\n",
            format(nrow(units), big.mark = ","), median(units$total)))
cat(sprintf("hexagon x gene matrix: %d x %d, %s nonzeros\n",
            nrow(X), ncol(X), format(length(X@x), big.mark = ",")))
```

The transcript density of the whole section, one point per hexagon.

A note on all the maps in this document: each hexagon is drawn as a small
square centred on the hexagon, not as a true hexagon, and the square's size
(`cex` in the plotting calls) is a display choice. It is set per figure by eye,
about 0.08 for the small per-topic panels and 0.12 to 0.16 for the larger maps.
Too small a size leaves gaps between hexagons that show up as a washed-out,
grainy look or faint stripes (compared side by side for one gene in the tumor-marker section); larger sizes make neighbouring squares overlap slightly, which makes the
maps look smoother than the underlying 12 um units. Points are drawn in ascending
order of the plotted value where a continuous value is shown, so the highest
values sit on top. The maps show values per 12 um hexagon, not per cell.


```{r}
#| fig-height: 6.6
pal <- hcl.colors(100, "Inferno")
lt <- log10(units$total)
spatial_plot(units$x, units$y, scale_col(lt, pal), cex = 0.14,
             main = sprintf("Transcripts per 12 um hexagon (log10, %.1f to %.1f)",
                            min(lt), max(lt)))
```

## 6. `topic-model`

Twelve factors, with control probes excluded from the feature space.

```{r}
model <- punkst_topic_model(hex, n_topics = 12, n_epochs = 2, sort_topics = TRUE,
                            min_count_per_feature = 100, min_count_train = 20,
                            exclude_feature_regex = control_re,
                            transform = TRUE, threads = threads, seed = 1)
B <- punkst_read_model(model)          # genes x topics
res <- punkst_read_topics(model)       # hexagons x topics
K <- ncol(B)
tcols <- colnames(B)
cat(sprintf("model: %d genes x %d topics; results: %s hexagons\n",
            nrow(B), K, format(nrow(res), big.mark = ",")))
stopifnot(K == 12, nrow(res) > 100000)
```

### Interpreting the factors

Each topic's top genes are those that are both abundant in the topic and specific
to it. To name the topics we score each one against a small set of marker genes
for breast tissue compartments. These sets were written by hand after looking at
the topics, so this is a heuristic labelling for orientation only; a
pre-specified mapping follows further down.

```{r}
share  <- B / rowSums(B)                       # fraction of each gene's mass in each topic
within <- sweep(B, 2, colSums(B), "/")         # P(gene | topic)
markers <- list(
    "tumor epithelium"   = c("ERBB2", "KRT7", "EPCAM", "FOXA1", "GATA3", "KRT8"),
    "fibroblast/stroma"  = c("LUM", "POSTN", "PDGFRB", "PDGFRA", "MMP2", "CCDC80"),
    "T cell"             = c("CD3E", "TRAC", "IL7R", "CD8A", "CD3D", "CD2"),
    "macrophage/myeloid" = c("LYZ", "CD163", "CD68", "AIF1", "MRC1", "FCER1G"),
    "endothelial"        = c("VWF", "PECAM1", "AQP1", "CD93", "CLEC14A"),
    "myoepithelial/SMC"  = c("MYH11", "ACTA2", "KRT5", "KRT14", "MYLK"),
    "plasma/B cell"      = c("MZB1", "CD79A", "SLAMF7"))
markers <- lapply(markers, function(g) g[g %in% rownames(B)])
score <- sapply(markers, function(g) colMeans(share[g, , drop = FALSE]))   # topics x compartments

labels <- vapply(seq_len(K), function(i) {
    b <- which.max(score[i, ])
    if (score[i, b] > 0.3) colnames(score)[b] else "mixed"
}, "")

top_genes <- function(k, n = 6) names(sort(within[, k] * share[, k], decreasing = TRUE))[seq_len(n)]
data.frame(topic = tcols,
           `share of transcripts` = sprintf("%.1f%%", 100 * colSums(B) / sum(B)),
           `marker-based label` = labels,
           `top genes` = vapply(tcols, function(k) paste(top_genes(k), collapse = ", "), ""),
           check.names = FALSE, row.names = NULL)
```

```{r}
#| fig-width: 11
#| fig-height: 5
genes_order <- unique(unlist(lapply(tcols, top_genes)))
m <- t(share[genes_order, ])
rownames(m) <- sprintf("%s: %s", tcols, labels)
heat(m, main = "Top genes per topic (fraction of the gene's transcripts in the topic)",
     zlim = c(0, 1), cex_col = 0.55)
```

## 7. Factors in space

Each hexagon coloured by its most probable topic:

```{r}
#| fig-width: 10
#| fig-height: 6.6
P <- as.matrix(res[, tcols])
top <- max.col(P, ties.method = "first")            # index into topics
pal_t <- hcl.colors(K, "Dark 3")
op <- par(mar = c(4, 4, 2, 13), xpd = NA)
spatial_plot(res$x, res$y, pal_t[top], cex = 0.14, main = "Most probable topic per hexagon")
legend("topright", inset = c(-0.3, 0), pch = 15, col = pal_t, bty = "n", cex = 0.75,
       legend = sprintf("%s: %s", tcols, labels))
par(op)
```

The tissue separates into tumour epithelium, stromal and immune compartments. To
see each factor on its own, here is the per-hexagon probability of every topic:

```{r}
#| fig-width: 13
#| fig-height: 8.4
op <- par(mfrow = c(3, 4), mar = c(1, 1, 2, 1))
pal <- hcl.colors(100, "viridis")
for (i in seq_len(K)) {
    o <- order(P[, i])                                # draw high probabilities last
    spatial_plot(res$x[o], res$y[o], scale_col(P[o, i], pal, 0, 1), cex = 0.08,
                 main = sprintf("%s: %s", tcols[i], labels[i]), axes = FALSE, xlab = "", ylab = "")
}
par(op)
```

### Spatial coherence check

If the factors reflect real tissue structure, neighbouring hexagons should share a
top topic far more often than chance (single 12 um hexagons are noisy, so well
below 100%). The hexagon centres form a regular lattice, so the six neighbours of
each hexagon are found from the lattice offsets, taken here from the hexagon
nearest the centre of the section. As a reference we repeat the statistic after
randomly permuting the topic labels.

```{r}
d <- 12
c0 <- which.min((res$x - median(res$x))^2 + (res$y - median(res$y))^2)
dist0 <- sqrt((res$x - res$x[c0])^2 + (res$y - res$y[c0])^2)
nb0 <- which(dist0 > 0 & dist0 < 1.2 * d)
offsets <- cbind(dx = res$x[nb0] - res$x[c0], dy = res$y[nb0] - res$y[c0])
stopifnot(nrow(offsets) == 6)

agreement <- function(lab) {
    hits <- unlist(lapply(seq_len(6), function(j) {
        nb <- match_xy(res$x + offsets[j, "dx"], res$y + offsets[j, "dy"],
                       res$x, res$y, digits = 1)
        (lab[nb] == lab)[!is.na(nb)]
    }))
    mean(hits)
}
agree <- agreement(top)
set.seed(0)
agree_perm <- agreement(sample(top))
cat(sprintf("neighbours sharing the top topic: %.1f%%  (permuted labels: %.1f%%)\n",
            100 * agree, 100 * agree_perm))
stopifnot(agree > 0.4, agree > 2 * agree_perm)
```

## Reanalysis with an external marker mapping

The marker sets used above were written after looking at the topics, so they are
not an independent check. Here we repeat the annotation with a fixed, pre-specified
mapping of 13 breast tissue compartments, defined before looking at this
dataset's topics. Not every gene is on the Xenium panel, so we first report
coverage.

```{r}
ref_markers <- list(
    "epithelium (luminal/tumor)" = c("EPCAM", "KRT8", "KRT18", "KRT19", "KRT7", "CDH1", "FOXA1"),
    "fibroblast"     = c("DCN", "LUM", "COL1A1", "COL1A2", "FBLN1", "PDGFRA"),
    "pericyte/vSMC"  = c("RGS5", "NOTCH3", "MYH11", "MCAM", "PDGFRB"),
    "myoepithelial"  = c("KRT5", "KRT14", "KRT17", "TP63", "OXTR"),
    "T cell"         = c("CD3E", "CD3D", "CD3G", "TRAC", "CD247"),
    "NK"             = c("NKG7", "GNLY", "KLRD1"),
    "macrophage"     = c("C1QA", "C1QB", "CD163", "CD68", "CSF1R", "MRC1"),
    "dendritic"      = c("CLEC9A", "LAMP3", "CD1C"),
    "mast"           = c("TPSAB1", "CPA3", "KIT"),
    "B cell"         = c("MS4A1", "CD79A", "CD79B", "CD19"),
    "plasma"         = c("MZB1", "JCHAIN", "XBP1", "IGKC"),
    "endothelial"    = c("PECAM1", "VWF", "CDH5", "PLVAP", "CLEC14A", "KDR"),
    "adipocyte"      = c("ADIPOQ", "PLIN1", "LEP"))
panel <- feat$feature[!is_ctrl]
ref_present <- lapply(ref_markers, function(g) g[g %in% panel])
cat(sprintf("%d of %d genes are on the panel\n",
            sum(lengths(ref_present)), sum(lengths(ref_markers))))
data.frame(compartment = names(ref_markers),
           `on panel` = sprintf("%d/%d", lengths(ref_present), lengths(ref_markers)),
           missing = vapply(names(ref_markers), function(c) {
               m <- setdiff(ref_markers[[c]], panel)
               if (length(m)) paste(m, collapse = ", ") else "-"
           }, ""), check.names = FALSE, row.names = NULL)
```

### Topic-level scores

For each topic and compartment we average, over the compartment's on-panel genes,
the log2 enrichment of the gene in the topic: the fraction of the gene's
transcripts assigned to the topic divided by the topic's overall share. A value of
1 means the marker is twice as concentrated in that topic as expected by chance.
A topic is assigned to a compartment when its best score exceeds 1.

```{r}
#| fig-width: 10
#| fig-height: 5
topic_frac <- colSums(B) / sum(B)
enr <- log2(sweep(share + 1e-3, 2, topic_frac, "/"))
ref_score <- sapply(ref_present, function(g) colMeans(enr[g, , drop = FALSE]))  # topics x compartments

ref_labels <- vapply(seq_len(K), function(k) {
    b <- which.max(ref_score[k, ])
    if (ref_score[k, b] > 1) colnames(ref_score)[b] else "unassigned"
}, "")

m <- ref_score
rownames(m) <- sprintf("%s: %s", tcols, ref_labels)
heat(m, main = "Topic x compartment marker enrichment (pre-specified mapping)",
     zlim = c(-3, 3), pal = rev(hcl.colors(50, "RdBu")))

data.frame(topic = tcols, `hand-picked label` = labels,
           `pre-specified label` = ref_labels,
           `best score` = round(apply(ref_score, 1, max), 2),
           check.names = FALSE, row.names = NULL)
```

### Hexagon-level check that does not use the topic model

To check the assignment against the raw counts rather than the fitted topics, we
weight each gene by its inverse total count so abundant genes do not dominate, and
give each hexagon the compartment with the highest mean marker signal. This is
compared with the compartment assigned to the hexagon's most probable topic.
Hexagons in the results file are matched to the count matrix by their (x, y)
centre, because punkst's random keys are not unique.

```{r}
#| fig-width: 10
#| fig-height: 4.6
gene_tot <- Matrix::colSums(X)
Xw <- X %*% Matrix::Diagonal(x = 1 / pmax(gene_tot, 1))
colnames(Xw) <- colnames(X)
comp_names <- names(ref_present)
comp_sig <- sapply(comp_names, function(cn)
    Matrix::rowMeans(Xw[, ref_present[[cn]], drop = FALSE]))
comp_sig <- sweep(comp_sig, 2, colSums(comp_sig), "/")     # comparable across compartments
direct <- comp_names[max.col(comp_sig, ties.method = "first")]
direct[rowSums(comp_sig) == 0] <- "none"

ridx <- match_xy(res$x, res$y, units$x, units$y)            # results row -> row of X
stopifnot(!anyNA(ridx))

topic_label <- ref_labels[top]
direct_r <- direct[ridx]
ok <- topic_label != "unassigned" & direct_r != "none"
tl <- topic_label[ok]; dl <- direct_r[ok]
agree_ref <- mean(tl == dl)
set.seed(0)
agree_shuf <- mean(sample(tl) == dl)
cat(sprintf("%s hexagons compared; direct marker call matches topic-derived label for %.1f%% (shuffled: %.1f%%)\n",
            format(sum(ok), big.mark = ","), 100 * agree_ref, 100 * agree_shuf))

cm <- table(tl, dl)
cm <- unclass(cm / rowSums(cm))
heat(cm, main = "Row fraction: compartment from top topic (rows) vs raw marker counts (columns)",
     zlim = c(0, 1))
```

### Map of the pre-specified annotation

```{r}
#| fig-width: 10
#| fig-height: 6.8
uniq <- sort(unique(ref_labels))
pal2 <- setNames(hcl.colors(length(uniq), "Dark 3"), uniq)
pal2["unassigned"] <- "grey80"
op <- par(mar = c(4, 4, 2, 13), xpd = NA)
spatial_plot(res$x, res$y, pal2[topic_label], cex = 0.14,
             main = "Hexagons coloured by the pre-specified compartment of their top topic")
legend("topright", inset = c(-0.3, 0), pch = 15, col = pal2, bty = "n", cex = 0.75, legend = names(pal2))
par(op)
```

**Reading the result.** In the run this vignette was written from, the
pre-specified mapping agreed with the hand-picked labels for the compartments with
several on-panel markers and a distinct signature (T cell, B cell, endothelial,
myoepithelial, fibroblast). It did not reproduce the tumor labels: the main tumor
topic scored just below the assignment threshold and other tumor-rich topics
received low-support labels such as plasma, mast or adipocyte, each resting on one
to three low-count genes (plasma has only MZB1 on the panel). The hexagon-level
agreement with raw marker counts was well above a shuffled baseline but modest in
absolute terms. In a tumor-dominated section, with 41 of 60 markers on a 313-gene
panel, this mapping is better suited to the immune, vascular and stromal
compartments than to separating tumor from normal epithelium, and its labels for
small, weakly supported compartments should not be over-interpreted. A
reference-based method with cell-level reference profiles would be the stronger
test. Check the numbers above against these statements when you re-run.

## Tumor markers in space

The panel includes the HER2 gene `ERBB2`, the hormone receptors `ESR1` and `PGR`,
the luminal-lineage genes `FOXA1` and `GATA3`, the proliferation marker `MKI67`,
and the basal keratin `KRT5`. `GRB7` (usually co-amplified with `ERBB2`) is not on
the panel, so HER2-axis evidence rests on `ERBB2` alone. Expression here is
transcripts per 1,000 transcripts in each 12 um hexagon.

```{r}
tumor_genes <- c("ERBB2", "ESR1", "PGR", "FOXA1", "GATA3", "MKI67", "KRT5")
cat("not on panel:", setdiff("GRB7", dictionary), "\n")
tot <- units$total
rate <- sapply(tumor_genes, function(g) as.numeric(X[, g]) / pmax(tot, 1) * 1000)
round(data.frame(
    transcripts = Matrix::colSums(X[, tumor_genes]),
    `% hexagons with >=1` = 100 * colMeans(rate > 0),
    `99th pct rate / 1000` = apply(rate, 2, quantile, probs = 0.99),
    check.names = FALSE), 2)
```

```{r}
#| fig-width: 16
#| fig-height: 8
op <- par(mfrow = c(2, 4), mar = c(1, 1, 2, 1), bg = "white")
pal <- hcl.colors(100, "inferno")
for (g in tumor_genes) {
    v <- rate[, g]
    o <- order(v)                                     # draw high-expressing hexagons last
    vmax <- if (any(v > 0)) max(quantile(v[v > 0], 0.99), 1e-9) else 1
    spatial_plot(units$x[o], units$y[o], scale_col(v[o], pal, 0, vmax), cex = 0.16,
                 main = sprintf("%s (colour scale 0 to %.1f)", g, vmax),
                 axes = FALSE, xlab = "", ylab = "")
}
par(op)
```

### Marker size and striping

The maps above use `cex = 0.16`. Here is the same `ERBB2` map drawn with
`cex = 0.1` on the left and `cex = 0.16` on the right, to show the effect of the
marker size described earlier. With the smaller squares the map looks washed out and grainy, and
horizontal striping along the rows of hexagons can appear (it was pronounced in
the 2 x 4 layout of the maps above when they were first drawn with this size),
because the squares do not fully cover the spacing between hexagons and the
background shows through. The data are identical in both panels.

```{r}
#| fig-width: 14
#| fig-height: 5.6
v <- rate[, "ERBB2"]
o <- order(v)
vmax <- max(quantile(v[v > 0], 0.99), 1e-9)
pal <- hcl.colors(100, "inferno")
op <- par(mfrow = c(1, 2), mar = c(1, 1, 2, 1))
for (cx in c(0.1, 0.16))
    spatial_plot(units$x[o], units$y[o], scale_col(v[o], pal, 0, vmax), cex = cx,
                 main = sprintf("ERBB2, cex = %.2f", cx), axes = FALSE, xlab = "", ylab = "")
par(op)
```

Do the tumor genes sit where the epithelial topics are? Mean rate by the
pre-specified compartment of each hexagon's top topic:

```{r}
by <- as.data.frame(rate[ridx, ])
by$compartment <- topic_label
agg <- aggregate(. ~ compartment, data = by, FUN = mean)
agg[tumor_genes] <- round(agg[tumor_genes], 2)
agg$hexagons <- as.integer(table(by$compartment)[agg$compartment])
agg
```

Receptor status is a clinical determination from IHC or ISH on pathology and
cannot be called from this panel. Low `ESR1`/`PGR` counts in particular are not
evidence of receptor negativity, because these genes are often weakly detected by
Xenium. These maps show where the transcripts are, not a clinical subtype.

## Summary

```{r}
data.frame(
    stage = c("SpatialData read", "export (intrinsic um, qv >= 20)", "pts2tiles",
              "tiles2hex", "topic-model", "spatial coherence"),
    result = c(sprintf("%s transcripts, zarr store", format(tx$rows, big.mark = ",")),
               sprintf("%s transcripts written", format(n_kept, big.mark = ",")),
               sprintf("%d features, %d genes", nrow(feat), sum(!is_ctrl)),
               sprintf("%s hexagons at 12 um", format(nrow(units), big.mark = ",")),
               sprintf("%d topics; labels from marker genes", K),
               sprintf("%.0f%% of neighbours share a top topic (permuted: %.0f%%)",
                       100 * agree, 100 * agree_perm)))
```
